Understanding the Landscape of Childlessness in the U.S.

### 2024-03-20 outputs/paper/paper.qmd
update paper

Overall, the data shows an increase in childlessness across all health levels and conditions approaching 2020. As mentioned, @fig-nochild-health-marital shows that people with excellent health have the highest percentage of childlessness, having a 10.49% increase throughout the 50-year period (28.26% in 1972 to 38.75% in 2022). People with good and fair health exhibit a similar rate of childlessness in 2022, at about 30%. However, people with poor health, once having the lowest rate of childlessness (at 12.27% in 1972), now increases to 20.40% in 2022, which translates to a substantial 8.13% increase. Overall, on average, across all health levels from 1972-2022, @fig-avg-one shows that the percentage of childlessness increases at about 6.836%.

@@

As for marital status, @fig-nochild-health-marital demonstrates that a significant portion of people who have never married are childless. However, more and more people are reluctant to get married but still have children. This is observable in the childlessness percentage decrease of people who never marry, decreasing from 96.73% in 1972 to 72.53% in 2022. For people who are divorced, separated and widowed, this percentage is on the rise fluctuates, displaying the complex dynamics between these relationship statuses and childbearing. For married people though, this childlessness percentage also decreases, from 10.51% in 1972 to 13.97% in 2022. Overall, on average, across all marital statuses from 1972-2022, @fig-avg-one shows that the percentage of childlessness decreases to about 7.39%.

@@

While all classes show an increase in childlessness in @fig-nochild-class-edu, the data suggests the most significant rise occurred among the lower class, with their percentage of childless individuals nearly doubling from approximately 17.16% in 1972 to around 34.46% in 2022, marking a substantial increase of approximately 101.04% over the specified period. The working class also experienced a significant increase, from around 21.83% in 1972 to approximately 31.44% in 2022, indicating a rise of roughly 43.98%. Additionally, the middle class saw a slight increase, from approximately 28.24% in 1972 to about 30.09% in 2022, representing a rise of approximately 6.55%. Similarly, the upper class saw an increase, with their percentage of childless individuals climbing from approximately 20.24% in 1972 to about 27.87% in 2022, indicating an increase of roughly 37.71%.

@@

Similarly, data reveals a distinct pattern across educational groups. Individuals with a high school diploma consistently exhibit the highest percentage of childlessness throughout the entire period, ranging from around 28.15% in 1972 to 34.56% in 2022. Conversely, the percentage of childless individuals with a college and higher degree has decreased from 32.85% in 1972 to 29.84% in 2022. The trend for individuals with less than a high school education increased from 16.97% in 1972 to 22.90% in 2022.

@@

```{r}
#| include: false
# Calculate the correlation coefficient
correlation <- cor(data_long_overall$Year, data_long_overall$Percentage)

# Print the correlation coefficient
print(paste("Correlation coefficient between Year and Percentage:", correlation))
```

>>>>

Overall, the data shows an increase in childlessness across all health levels and conditions approaching 2020. As mentioned, @fig-nochild-health-marital shows that people with excellent health have the highest percentage of childlessness, having a 10.49% increase throughout the 50-year period (28.26% in 1972 to 38.75% in 2022). People with good and fair health exhibit a similar rate of childlessness in 2022, at about 30%. However, people with poor health, once having the lowest rate of childlessness (at 12.27% in 1972), now increases to 20.40% in 2022, which translates to a substantial 8.13% increase. Overall, on average, across all health levels from 1972-2022, @fig-avg-one shows that the percentage of childlessness increases at about 6.836%. Observable from the graph, health as a factor is positively correlated to childlessness.

@@

As for marital status, @fig-nochild-health-marital demonstrates that a significant portion of people who have never married are childless. However, more and more people are reluctant to get married but still have children. This is observable in the childlessness percentage decrease of people who never marry, decreasing from 96.73% in 1972 to 72.53% in 2022. For people who are divorced, separated and widowed, this percentage is on the rise fluctuates, displaying the complex dynamics between these relationship statuses and childbearing. For married people though, this childlessness percentage also decreases, from 10.51% in 1972 to 13.97% in 2022. Overall, on average, across all marital statuses from 1972-2022, @fig-avg-one shows that the percentage of childlessness decreases to about 7.39%. Observable from the graph, marital status as a factor is negatively correlated to childlessness.

@@

While all classes show an increase in childlessness in @fig-nochild-class-edu, the data suggests the most significant rise occurred among the lower class, with their percentage of childless individuals nearly doubling from approximately 17.16% in 1972 to around 34.46% in 2022, marking a substantial increase of approximately 101.04% over the specified period. The working class also experienced a significant increase, from around 21.83% in 1972 to approximately 31.44% in 2022, indicating a rise of roughly 43.98%. Additionally, the middle class saw a slight increase, from approximately 28.24% in 1972 to about 30.09% in 2022, representing a rise of approximately 6.55%. Similarly, the upper class saw an increase, with their percentage of childless individuals climbing from approximately 20.24% in 1972 to about 27.87% in 2022, indicating an increase of roughly 37.71%. Overall, on average, across all socio-economic clases from 1972-2022, @fig-avg-two shows that the percentage of childlessness increases at about 9.21%. Observable from the graph, class as a factor is positively correlated to childlessness.

@@

Similarly, @fig-nochild-class-edu reveals a distinct pattern across educational groups. Individuals with a high school diploma consistently exhibit the highest percentage of childlessness throughout the entire period, ranging from around 28.15% in 1972 to 34.56% in 2022. Conversely, the percentage of childless individuals with a college and higher degree has decreased from 32.85% in 1972 to 29.84% in 2022. The trend for individuals with less than a high school education increased from 16.97% in 1972 to 22.90% in 2022. Overall, on average, across all educational levels from 1972-2022, @fig-avg-two shows that the percentage of childlessness increases at about 3.11%. Observable from the graph, educational attainment as a factor is slightly positively correlated to childlessness.

@@
